\textbf{\LARGE{Vatya Kishore}} \hfill (647) 860-0369\\
11 - 1591 Lycée Place Ottawa, ON, K1G 4A7 \hfill vkish067@uottawa.ca\\
\newline

\noindent
\textbf{\large{BIO}}\\
Vatya is a Undergraduate student at the University of Ottawa. Currently enrolled as a fourth year student in the Joint Honours B.Sc. in Mathematics and Economics program. He has honed analytical skills and gained basic proficiency in Stata and R through Economics and Mathematics university course work. He also gained intermediate proficiency in Java and Python from course work throughout high school and a couple of courses in university, and has been awarded with a certificate of excellence for participating in the Canadian Computing Competition.\par He has built strong professional communications skills while working at Enterprise Holdings, Hudson's Bay and Ontario Consumers Home Services (OCHS), through daily communications with employees and customers. Improved leadership and organisational skills while training some of the new employees at OCHS and as a team lead on multiple occasions at Enterprise Holdings. He has worked as a volunteer at the Residents’ Association University of Ottawa (RAUO) as a Floor Representative where he helped coordinate multiple RAUO events and RAUO elections. He has also volunteered as a peer tutor in high school.\\

{\parindent0pt
\textbf{\large{SKILLS}}\\
\raisebox{0.25ex}{\tiny$\bullet$} Honed analytical skills through Mathematics, Statistic and Econometric courses \\
\raisebox{0.25ex}{\tiny$\bullet$} Basic LaTex, R and Stata proficiency \\
\raisebox{0.25ex}{\tiny$\bullet$} Intermediate Java and Python proficiency \\ 
\raisebox{0.25ex}{\tiny$\bullet$} Other skills: Adobe Photoshop, MS Office \\
\raisebox{0.25ex}{\tiny$\bullet$} Certified Sales Force Administrator \\

\textbf{\large{SELECTED ACHIEVEMENTS}}\\
\textbf{Certificate of Excellence}, Canadian Computing Competition, University of Waterloo, 2013\\
\textbf{Deans Honours List}, University of Ottawa, Fall 2018 and Winter 2019\\

\textbf{\large{OTHER EXPERIENCE}}\\
\textbf{Part-Time Driver}\hfill 2015 – 2016\\
Enterprise Holdings Inc. Ottawa, ON\\
\raisebox{0.25ex}{\tiny$\bullet$} Worked in groups of two to six including a lead delivering cars to different enterprise locations throughout Ottawa and some parts of Ontario\\
\raisebox{0.25ex}{\tiny$\bullet$} Improved people management and organisational skills through taking the role of team lead on several occasions\\
\raisebox{0.25ex}{\tiny$\bullet$} Learned to navigate through the city efficiently without a GPS\\
\raisebox{0.25ex}{\tiny$\bullet$} Built strong professional communication skills through daily interaction with multiple employees and customers \\

\textbf{Fulfilment Associate}\hfill 2014\\
Hudson Bay Co., Toronto, ON\\
\raisebox{0.25ex}{\tiny$\bullet$} Gained management and organisational skills through inventory pricing and stocking\\
\raisebox{0.25ex}{\tiny$\bullet$} Improved communication skills while helping customers locate items and directing them to the right salesperson\\
 
\textbf{Door to Door Sales Associate} \hfill 2014\\ 	 	
Ontario Consumer Home Services, Toronto, ON\\
\raisebox{0.25ex}{\tiny$\bullet$} Built confidence and strong communication skills through daily sales and customer service interactions with customers while on sales route\\
\raisebox{0.25ex}{\tiny$\bullet$} Developed organisational, communication and leadership skills while training and supervising 4 of the trainees\\

\textbf{\large{EDUCATION}}\\
\textbf{Joint Honours Bachelor of Science in Mathematics and Economics}\\
University of Ottawa, ON\\
\raisebox{0.25ex}{\tiny$\bullet$} Currently enrolled as a full-time fourth year student\\ 
\raisebox{0.25ex}{\tiny$\bullet$} Relevant Courses: ECO3151 (Intro. to Econometrics) MAT2371 (Intro. to Probability), MAT2375 (Intro. to Statistics) ITI1120 (Intro. to Computing)\\
\raisebox{0.25ex}{\tiny$\bullet$} Expected graduation date: May 2020\\

\textbf{\large{PERSONAL}}\\
\textbf{Language}: Fluent in English and Hindi\\
\textbf{Photography}: Lead the school photography club in high school. Gained intermediate photography and editing skills through a photography course in high school\\
\textbf{Sports}: Built sense of sportsmanship and ability to work in teams through playing intramural soccer\\ 
\textbf{Hobbies}: Swimming, music, freestyle writing, photography\\
\textbf{Volunteer Experience}\\
\raisebox{0.25ex}{\tiny$\bullet$} Floor Representative (Floor 9 \& 10), Residents’ Association University of Ottawa\hfill 2014 – 2015\\
\raisebox{0.25ex}{\tiny$\bullet$} Peer Tutor, Leaside High School, Toronto\hfill 2012 – 2014\\

}